\documentclass[]{letter}


\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{The Editorial Office \\ Journal of Scheduling}
\address{	
    Helga Ingimundardottir\\
    University of Iceland\\
    Dunhaga 5, IS-107 Reykjavik, Iceland\\
}

\opening{Dear JOSH Editors,}

We would like submit a revised version of our paper titled: ``Discovering 
dispatching rules from data using imitation learning: Case study for the 
job-shop problem'' -- manuscript \texttt{JOSH-D-15-00213}.

The answers from the two anonymous reviewers and associate editor's note are as 
follows:
\begin{description}
    \item[Reviewer 1] remarks: 
    
    \begin{itemize}
    \item Finding or creating proper dispatching rules is the key to solve 
    middle to large scale factory job scheduling problems.
    \item The paper focuses on how to make decision based on the historic data 
    and build several models with different optimal approaches and parameters. 
    The simulation results indicates the models could give the reasonable 
    solution in the particular circumstance. The impacts of the optimal 
    approaches and parameters are also discussed.
    \item The paper did not mention the performance of the algorithm, such as 
    the calculation time, and the requirements of the computer. Normally such 
    performance are valuable for estimating the algorithm in practice.
    \item But anyway I suppose the paper is good for publishing.
    \end{itemize}    
    \item[Reviewer 2] remarks: 
    \begin{enumerate}
    \item There are many language and format errors in this paper, such as 
    unnecessary comma or missing hyphen.    
    \item Full of spell mistakes and grammatical errors. (in page 2, line 21, 
    column 2 "featues (features)" or line 28 in same column "rules is(are)")    
    \item Unreadable, This paper needs to be proofread thoroughly. (In page 2, 
    first column sentence in line 45 and 46 is obscure)
    \end{enumerate}

    \item[Associate editor] The two reviewers have opposing views.
    Reviewer 1 recommends accept, but is not without reservation.
    Reviewer 2 finds the paper difficult to read.
    Personally I find this paper technically interesting. I would like to see 
    it published eventually, but writing must be significantly improved. Not 
    only should English be improved. The authors should make the material 
    easier to digest by the readers.   
    
\end{description}
Based on the advice received from the editor our paper has been professionally 
proofread. 
Moreover, in order to make the material easier to digest for the reader, 
we have made the paper more readable by reducing mathematical notation and 
describing more thoroughly in the main text equations, symbols, and pseudocodes.

Computational times have been addressed. These computational times are with 
respect to training times, or the time needed to create the dispatching rules 
which may take days. The dispatching rules themselves are as fast as any other 
commonly implemented dispatching rule, such as MWR. In practice the 
application of these rules is very fast and therefore of great practical 
importance.


\signature{Helga Ingimundardottir}

\closing{Sincerely}

%enclosure listing
%\encl{Summary of changes with diffs from submitted to revised version.}

\end{letter}
\end{document}
